---
title: "Covid-19 Tracker"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: paper
---

# Global
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(global_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(global_deaths_plot)
```

## Column {data-width=350}
   
### Total Cases

```{r}
valueBox(add_commas(sum(cases_by_country_df$cases)), icon = "glyphicon-stats", color = "white")
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(sum(deaths_by_country_df$deaths)), icon = "glyphicon-warning-sign", color = "white")
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# US
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(US_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(US_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(US_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(US_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# Italy
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(Italy_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(Italy_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(Italy_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(Italy_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# Spain
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(Spain_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(Spain_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(Spain_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(Spain_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# Germany
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(Germany_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(Germany_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(Germany_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(Germany_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# China
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(China_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(China_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(China_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(China_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# France
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(France_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(France_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(France_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(France_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```

# Iran
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
ggplotly(Iran_cases_plot)
```

### Covid-19 Deaths
    
```{r}
ggplotly(Iran_deaths_plot)
```

## Column {data-width=350}
   
### Total Confirmed Cases

```{r}
valueBox(add_commas(Iran_total_cases, icon = "glyphicon-stats", color = "white"))
```   
 
### Total Deaths
    
```{r}
valueBox(add_commas(Iran_total_deaths, icon = "glyphicon-warning-sign", color = "white"))
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df, options = list(pageLength = 10,
                                                     info = FALSE))
```
