---
title: "covid-19"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cosmo
---

# Global
    
## Column {data-width=650, .tabset .tabset-fade}
    
### Covid-19 Cases
    
```{r}
global_cases_plot
```

### Covid-19 Deaths
    
```{r}
global_deaths_plot
```

## Column {data-width=350}
   
### Total Cases

```{r}
valueBox(sum(cases_by_country_df$cases), icon = "glyphicon-stats", color = "red")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(deaths_by_country_df$deaths), icon = "glyphicon-warning-sign", color = "red")
```

### Cases and Deaths by Country
    
```{r}
datatable(deaths_cases_by_country_df)
```


# US
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}
   
### Total Confirmed Cases

```{r}
valueBox(US_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(US_total_deaths, icon = "glyphicon-warning-sign")
```

# Italy
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}
   
### Total Confirmed Cases

```{r}
valueBox(Italy_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(Italy_total_deaths, icon = "glyphicon-warning-sign")
```

# Spain
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Total Confirmed Cases

```{r}
valueBox(Spain_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(Spain_total_deaths, icon = "glyphicon-warning-sign")
```

# Germany
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Total Confirmed Cases

```{r}
valueBox(Germany_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(Germany_total_deaths, icon = "glyphicon-warning-sign")
```

# China
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}
   
### Total Confirmed Cases

```{r}
valueBox(China_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(China_total_deaths, icon = "glyphicon-warning-sign")
```

# France
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300} 
   
### Total Confirmed Cases

```{r}
valueBox(France_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(France_total_deaths, icon = "glyphicon-warning-sign")
```

# Iran
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}
   
### Total Confirmed Cases

```{r}
valueBox(Iran_total_cases, icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(Iran_total_deaths, icon = "glyphicon-warning-sign")
```

