---
title: "covid-19"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: readable
---

# Global
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# US
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# Italy
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# Spain
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# Germany
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# China
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# France
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

# Iran
    
## Column {data-width=700, .tabset}
    
### Covid-19 Confirmed Cases
    
```{r}
```

### Covid-19 Deaths
    
```{r}
```

## Column {data-width=300}

### Last Updated

```{r}
valueBox(today(tzone = "Europe/London"), icon = "glyphicon-calendar")
```   
   
### Total Confirmed Cases

```{r}
valueBox(sum(US_df$cases), icon = "glyphicon-stats")
```   
 
### Total Deaths
    
```{r}
valueBox(sum(US_df$deaths, na.rm=T), icon = "glyphicon-warning-sign")
```

